Learning and comparing functional connectomes across subjects

### 2013-01-01 paper.tex
typo

Predictive modeling is concerned with learning (or fitting) a model to
draw conclusion on new and unseen data \cite{pereira2009}. Typically on
brain imaging data, it opens the door to learning diagnosis or prognosis
markers \cite{stonnington2010}. However, beyond the practical use of
prediction, these models can also be useful to uncover mechanism of brain
function \cite{norman2006}. Both the fact that information \emph{can} be
drawn to generalize predictions to new data and \emph{how} or
\emph{where} informs us on brain function. Multivariate predictive models
are attractive in connectomics because they are sensitive to dependencies
between features and avoid the need to correct for multiple comparisons
since the significance of an entire pattern is evaluated using a single
statistical test. From the perspective of medical applications, using
resting-state connectivity as a biomarker is particularly appealing as it
can be applied to impaired patients \cite{greicius2008b}. Predictive
modeling techniques have been successfully applied to identify
connectome-based biomarkers of Alzheimer's disease
\cite{stonnington2010}, depression \cite{craddock2009}, schizophrenia
\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008}, aging
\cite{dosenbach2010}, as well as to classify mental operations
\cite{richiardi2011,shirer2012}.

@@

The interpretation of the predictive model can be complicated and
requires insight into the mechanisms
underlying the modeling approach. For linear classifiers, 
classifier weights are similar to the weight of a ordinary regression.
If features are appropriately
standardized prior to training, the magnitude of weights can be
interpreted to reflect the relative importance of the feature to the
model, but interpreting how the feature differs between classes or
relates to a continuous variable is more complicated, particularly given
the multivariate nature of their involvement.  For classification methods
such as Fisher's linear discriminant analysis (LDA), which maximally
separates class means given their standard deviation, feature weights are
representative of the differences between class means. For support vector
classification, classifier weights are derived from observations that are
the most similar between classes, and hence represents the border between
classes. To draw conclusions on the features used for prediction, it is
perhaps most reasonable to adapt a conservative interpretation in which
predictive models is used to identify the most relevant features that are
later tested in followon experiments better suited to elucidating their
relationship to the variable of interest.

>>>>

Predictive modeling is concerned with learning (or fitting) a model to
draw conclusions on new and unseen data \cite{pereira2009}. Typically on
brain imaging data, it opens the door to learning diagnosis or prognosis
markers \cite{stonnington2010}. However, beyond the practical use of
prediction, these models can also be useful to uncover mechanism of brain
function \cite{norman2006}. Both the fact that information \emph{can} be
drawn to generalize predictions to new data and \emph{how} or
\emph{where} informs us on brain function. Multivariate predictive models
are attractive in connectomics because they are sensitive to dependencies
between features and avoid the need to correct for multiple comparisons
since the significance of an entire pattern is evaluated using a single
statistical test. From the perspective of medical applications, using
resting-state connectivity as a biomarker is particularly appealing as it
can be applied to impaired patients \cite{greicius2008b}. Predictive
modeling techniques have been successfully applied to identify
connectome-based biomarkers of Alzheimer's disease
\cite{stonnington2010}, depression \cite{craddock2009}, schizophrenia
\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008}, aging
\cite{dosenbach2010}, as well as to classify mental operations
\cite{richiardi2011,shirer2012}.

@@

The interpretation of the predictive model can be complicated and
requires insight into the mechanisms
underlying the modeling approach. For linear classifiers, 
classifier weights are similar to the weights of a ordinary regression.
If features are appropriately
standardized prior to training, the magnitude of weights can be
interpreted to reflect the relative importance of the feature to the
model, but interpreting how the feature differs between classes or
relates to a continuous variable is more complicated, particularly given
the multivariate nature of their involvement.  For classification methods
such as Fisher's linear discriminant analysis (LDA), which maximally
separates class means given their standard deviation, feature weights are
representative of the differences between class means. For support vector
classification, classifier weights are derived from observations that are
the most similar between classes, and hence represents the border between
classes. To draw conclusions on the features used for prediction, it is
perhaps most reasonable to adapt a conservative interpretation in which
predictive models is used to identify the most relevant features that are
later tested in followon experiments better suited to elucidating their
relationship to the variable of interest.
